%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{structure} 

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage{xcolor}
\usepackage{fontspec}
\setmainfont[]{Roboto}
% \setmainfont[]{Arial}

\name{Tom Pollak} 

\begin{document}

\parbox{0.5\textwidth}{
    {\namesize\bf{Tom Pollak}} \\[6pt]
    York, UK\\
    \href{mailto:tompollak1000@gmail.com}{tompollak1000@gmail.com}
}
\hfill
\parbox{0.5\textwidth}{
    \vspace*{10pt}

    \begin{flushright}

        \href{https://github.com/tom-pollak}{github.com/tom-pollak} \\
        \href{https://tompollak.me}{tompollak.me} \\
        (+44) 77400 054268
    \end{flushright}

}

\smallskip
\hrule
\smallskip

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

    \begin{rSubsectionNoList}{University of York}{2023}{
            BEng. Computer Science -- Weighted average: 77\%
        }{}{}
    \end{rSubsectionNoList}

    \begin{rSubsectionNoList}{Lady Manners School}{2020}{
            A-Level --  Further Maths (A), Maths (A), Computer Science (A), Physics (A)
        }{}{}
    \end{rSubsectionNoList}

\end{rSection}

%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

    \begin{rSubsection}{Cisco Meraki}{June - August 2022}{Full Stack Software Engineer Intern -- Camera Intelligence Division}{London, UK}{}
        \item During my internship, I designed and implemented a deep learning model and pipeline proof of concept which allows users
        to search for \emph{anything} in a video feed -- a useful feature for the "Smart" Cisco Meraki CCTV cameras.
        \item For example, "A man wearing a chequered shirt and a backpack riding a bike"
        \item Used an \emph{\href{https://openai.com/blog/clip/}{OpenAI CLIP}} derivative to produce embeddings
        to index using \emph{\href{https://github.com/spotify/annoy}{Spotify's Annoy library}}.
        \item Extended the current on-camera motion detection pipeline to feed image "blobs" into the new model.
        \item Implemented in C++, using PyTorch and NCNN deep learning frameworks.
        \item A large challenge was the memory constraints of the edge devices -- the model could not be larger than 80MB.
        To address this I split the model between the camera and the server,
        all image processing and indexing is done on camera, with the server creating the text embedding from a user query.
        \item Once indexed, a busy 30 minute video could be queried in 0.2 seconds, with a total of 20MB index size.
        \item Attribute search was a hot request for many customers, most notably a for sale in all Starbucks restaurants.
        \item \href{https://gist.githubusercontent.com/tom-pollak/1a2e8c1fc61ba269e25c73c02c78007c/raw/45c8cbceda8cd745d6d00cb16a09979778df663b/gistfile1.txt}{\color{blue}{Project Reference}}
    \end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	PROJECTS
%----------------------------------------------------------------------------------------

\begin{rSection}{Projects}

    \begin{rSubsection}{Automated Horse Betting Software}{December 2020 - July 2021}{}{}{https://github.com/tom-pollak/each-way-matcher}
        \item Discovers undervalued horses by the bookmaker in each-way betting.
        \item Uses a strategy that the bookmaker calculates the odds of a horse
        "placing" (1st, 2nd or 3rd) using only the win odds of the that horse. This simplifies
        odds calculation for the bookies, but is not entirely accurate.
        \item Uses an adapted Kelly Criterion strategy with Expected Growth to calculate
        the optimal stake.
        \item Uses Python, Pandas and Selenium to scrape the horse races, interacts with
        Betfair API to place bets.
    \end{rSubsection}

    \begin{rSubsection}{Poker Web Application}{April 2019 - July 2020}{}{}{https://github.com/tom-pollak/web-poker}
        \item Free live poker web app, users can create accounts and tables, play poker, and chat with other players.
        \item Implemented in Python, with the Django web framework and a Postgres database,
        with web-sockets using Django Channels and Redis for real-time communication with users.
        Deployed with Docker and Heroku.
    \end{rSubsection}

    \begin{rSubsection}{SANS Institute}{August 2020}{FOR500 Windows Forensic Analysis}{}{https://www.sans.org/cyber-security-courses/windows-forensic-analysis}
        \item Sponsored by reaching the Elite stage of the Cyber Discovery programme.
    \end{rSubsection}

    \begin{rSubsection}{Cyber Discovery}{September 2018 - July 2019}{}{}{}
        \item Independently completed the Cyber Discovery programme, run by HM government.
        \item Selected as one of the top 500 (of 28,000) students to attend the Cyber Discovery Elite event in London.
    \end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------

\begin{rSection}{Skills}

    \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
        Languages    & Python, Rust, C++, Haskell, SQL, HTML.                                          \\
        Tools        & Linux, Git, VSCode, Neovim, SQLite, RegEx, {\fontfamily{lmr}\selectfont\LaTeX}. \\
        Technologies & GitHub, Docker, PyTorch, Numpy, Pandas, Matplotlib, Django, Selenium.           \\
    \end{tabular}

\end{rSection}

\end{document}
